---
title: "Continuos treatment"
autor: "Bertoni, Godfrin, Lim"
date:  11 February 20125
format:
  pdf: 
    fontsize: 9pt
    mainfont: Garamond
    sansfont: Garamond
editor: visual
output: 
  html_document:
    theme: cosmo
    latex_engine: pdflatex
    huxreg_options: "tabular={l|ccc}, tablewidth=0.1\\textwidth, tablefont=\\footnotesize"
    fig_caption: true
execute:
  echo: false
  warning: false
---

## Diff in Diff

```{r}
library(haven)
library(readxl)
library(tidyverse)
library(dplyr)
library(kableExtra)
Sys.setenv(RGL_USE_NULL = TRUE)

library(wooldridge)
library(DIDmultiplegtDYN)
library(huxtable)
library(plm)
library(Hmisc)
```

```{r}
tariffs_JDE <- read_dta("C:/Users/sarah/OneDrive/Desktop/Università/Econometria/Project/TLIndonesia2015/tariffs_JDE.dta")

panel_JDE <- read_dta("C:/Users/sarah/OneDrive/Desktop/Università/Econometria/Project/TLIndonesia2015/panel_JDE.dta")


```

## Indonesia dataset

```{r}
#data cleaning
PNL_TrIn <- panel_JDE %>%
  mutate(tarif_In_tr = as.numeric(tarif_inp_tri),
         year = as.numeric(year),
         distid = as.numeric(distid),
         prop=as.numeric(prop)) %>%
    rename(TarIn = tarif_In_tr) %>%
  select("year", "distid", "TarIn","p0", "age1660",  'hwage_e41', 'hwage_e42', 'hwage_e43', 'hwage_e44', 'hwage', 'work_e43', 'prop', 'p0', 'p1', 'p2')%>%
  drop_na() %>%
  mutate(TarIn = round(TarIn, digits=0))

#Won't display any graph as, well, too many districts. 

ChangeTrIn <- PNL_TrIn %>%
  group_by(distid) %>%
  mutate(CPY_TrIn = case_when(
    year == 1993 ~ 0,
    year == 1996 ~ (TarIn[year == 1996] - TarIn[year == 1993]),
    year == 1999 ~ (TarIn[year == 1999] - TarIn[year == 1996]),
    year == 2002 ~ (TarIn[year == 2002] - TarIn[year == 1999]),
    TRUE ~ NA_real_)) %>%
  ungroup() 

ChangeTrInp0_Wide <- ChangeTrIn %>%
  select(distid, year, CPY_TrIn, TarIn, p0,  'hwage_e41', 'hwage_e42', 'hwage_e43', 'hwage_e44', 'hwage', 'work_e43') %>%
  pivot_wider(
    names_from = year,
    values_from = c(CPY_TrIn, TarIn,p0),
    names_glue = "{.value}_{year}")

# Stayers ? 

ChangeTrIn_Stay <- ChangeTrIn %>% 
  mutate(Stayers = ifelse(year==1999 & CPY_TrIn==0, 1, 0))

huxreg("Stayers"=lm(data=ChangeTrIn_Stay, formula= Stayers ~ 1)) %>%  set_caption('Percentage of Stayers Indonesian Dataset')


model <-lm(data=na.omit(ChangeTrIn_Stay), formula= Stayers ~ 1)
names(model$coefficients)[1] = 'Stayers'
model<- huxreg(" "=model,
                  error_format = "({std.error})",
                  error_pos = "below",
                  statistics = c(N = "nobs"),
                  note = "{stars}",
                  align = "center") %>%
  set_caption('Percentage of Stayers Indonesian Dataset')


```

```{r}
# summary statistics
sum_stats_decile96 <- panel_JDE %>%
  select( p0, tarif_inp_tri, hwage_e43) %>% filter(panel_JDE$year=='1996')
sum_stats_decile99 <- panel_JDE %>%
  select(p0, tarif_inp_tri, hwage_e43) %>% filter(panel_JDE$year=='1999')

sum_stats_table_decile96 <- data.frame(
  Statistic = c("Mean", "SD", "Min", "Max", "N Obs"),
  sapply(sum_stats_decile96, function(x) c(
    mean = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    min = min(x, na.rm = TRUE),
    max = max(x, na.rm = TRUE),
    n_obs = sum(!is.na(x))
  ))
)

sum_stats_table_decile99 <- data.frame(
  Statistic = c("Mean", "SD", "Min", "Max", "N Obs"),
  sapply(sum_stats_decile99, function(x) c(
    mean = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    min = min(x, na.rm = TRUE),
    max = max(x, na.rm = TRUE),
    n_obs = sum(!is.na(x))
  ))
)


colnames(sum_stats_table_decile96) <- c("Statistic", "Poverty Headcount", "Input Tariff", "Wage (2nd education)" )

colnames(sum_stats_table_decile99) <- c("Statistic",  "Poverty Headcount", "Input Tariff", "Wage (2nd education)" )



sum_stats_table_decile96 <- sum_stats_table_decile96 %>%  mutate(Year= "1996")
sum_stats_table_decile99 <- sum_stats_table_decile99 %>%  mutate(Year= "1999")

## Combine
final_df <- rbind(sum_stats_table_decile96, sum_stats_table_decile99)
rownames(final_df) <- NULL

final_df %>% 
select(-Year)%>% kable(caption = "Summary Statistics of Indonesian Dataset in 1996 and 1999", digits = 2) %>%
  kable_classic_2(full_width = F, html_font = "Garamound") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  row_spec(0, bold = T) %>% pack_rows("1996",1,5)%>%
 pack_rows("1999",6,10) 
```

#### Ouput: Poverty

```{r}

df_summary <- panel_JDE %>%
  group_by(year, distid) %>%
  summarise(mean_poverty = mean(p0, na.rm = TRUE))  


# Density plot for years 1996 and 1999
ggplot(data = df_summary[df_summary$year %in% c(1996, 1999),], aes(x = mean_poverty, fill = factor(year))) +
  geom_density(alpha = 0.4) +  # Add density plot with transparency
  scale_fill_manual(values = c("1996" = "#69b3a2", "1999" = "#404080")) +  # Color for each year
  labs(x = "Mean Poverty", y = "Density", title = "Density Plot of Mean Poverty by Year") +
  theme_minimal() +
  ggtitle("Density of district Poverty in Indonesia for 1996 and 1999") +
  theme(
    plot.title = element_text(size = 10),     
    plot.subtitle = element_text(size = 9),  
    plot.caption = element_text(size = 9),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8)
  ) +
  theme(legend.title = element_blank())  # Remove legend title if needed

```

We estimate the effect of input tariff on district level poverty for the 1996-1999 period.

```{r}



summary <- (did_multiplegt_stat(
   df = PNL_TrIn,
   Y = "p0",
    ID = "distid",
    Time = "year",
     D = "TarIn",
     order = 2,
     estimator = c("waoss", "aoss"),
     estimation_method = "dr",
   placebo = T,
    aoss_vs_waoss = TRUE,
   twfe = 'same_sample'
   
 ))

data <- as.data.frame(summary$results) %>%
  filter(rownames(.) %in% c("AOSS", "WAOSS")) %>%
  mutate(Variable = rownames(data))

dataa <- data %>% pivot_longer(cols = c("table.Estimate", "table.SE"), names_to = "Metric", values_to = "Value") %>%
mutate(
Value = ifelse(Metric == "table.SE", paste0("(", round(Value, 5), ")"), round(Value, 5)), 
Metric = ifelse(Metric == "table.Estimate", "Estimate", "SE")
) %>%
mutate("Estimator" = ifelse(Metric == "SE", "", Variable)) %>% 
mutate("Lower Bound" = ifelse(Metric == "SE", "", round(table.LB.CI,5))) %>% 
mutate("Upper Bound" = ifelse(Metric == "SE", "", round(table.UB.CI,5))) %>% 
mutate("AS vs WAS pvalue" = ifelse(Metric == "SE", "", round(aoss_vs_waoss.pval.,5)
	)) 

dataa %>% 
select(Estimator, Value, "Lower Bound", "Upper Bound"
)%>% kable(caption= 'Poverty headcount') %>%
  kable_classic_2(full_width = F, html_font = "Garamound") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  %>%
  row_spec(0, bold = T) %>%  footnote('There are 188 switcher and 71 stayers in the period from 1996 to 1999; The t-test of the difference between the WAS and the AS returns a pvalue of 0.06756; district level data')
```

```         
```

We do not find statistical significant results.

#### Output: Wage

We estimate the effect of input tariff on district level wages for level of education. We find significant results only for wages of individuals holding secondary education.

```{r}

### WAGE SECONDARY EDUCATION ONLY SIGNIFICANT WAGE



summary2 <- (did_multiplegt_stat(
   df = PNL_TrIn,
   Y = "hwage_e43",
    ID = "distid",
    Time = "year",
     D = "TarIn",
     order = 2,
     estimator = c("waoss", "aoss"),
     estimation_method = "dr",
   placebo = T,
    aoss_vs_waoss = TRUE,
   twfe = 'same_sample'
   
 ))

data <- as.data.frame(summary2$results) %>%
  filter(rownames(.) %in% c("AOSS", "WAOSS")) %>%
  mutate(Variable = rownames(data))

dataa <- data %>% pivot_longer(cols = c("table.Estimate", "table.SE"), names_to = "Metric", values_to = "Estimate") %>%
mutate(
Estimate = ifelse(Metric == "table.SE", paste0("(", round(Estimate, 5), ")"), round(Estimate, 5)), 
Metric = ifelse(Metric == "table.Estimate", "Estimate", "SE")
) %>%
mutate("Estimator" = ifelse(Metric == "SE", "", Variable)) %>% 
mutate("Lower Bound" = ifelse(Metric == "SE", "", round(table.LB.CI,5))) %>% 
mutate("Upper Bound" = ifelse(Metric == "SE", "", round(table.UB.CI,5))) %>% 
mutate("AS vs WAS pvalue" = ifelse(Metric == "SE", "", round(aoss_vs_waoss.pval.,5)
	)) 

dataa %>% 
select(Estimator, Estimate
)%>% kable(caption= 'Log Hourly Wages - junior secondary education') %>%
  kable_classic(full_width = F, html_font = "Garamound")   %>%
  row_spec(0, bold = T) %>%  footnote('There are 188 switcher and 71 stayers in the period from 1996 to 1999; The t-test of the difference between the WAS and the AS returns a pvalue of 0.002793504; district level data') 
```

#### Output: Employment

We can also estimate the effect on employment, across different education levels; we do not find significant results.

```{r, fig.width=7, fig.height=3}

did_multiplegt_dyn(
    df = indonesia,
    outcome = "work_e43",
    group = "distid",
    time = "year",
    treatment = "TarIn",
    normalized = TRUE,
    graph_off = F
)
```

## Italian dataset

### 

```{r}
##Data tidying
##Prices
Principali_dati_IT1_167_742_DF_DCSP_NIC2B2015_1_1_0_1_ <- read_excel("Principali dati (IT1,167_742_DF_DCSP_NIC2B2015_1,1.0) (1).xlsx")
prices <- Principali_dati_IT1_167_742_DF_DCSP_NIC2B2015_1_1_0_1_
prices <- prices %>% mutate(Region=prices$...3)
prices<- prices[6:174,]
prices<- prices %>% mutate ('Prices'= prices$...4)%>% mutate('Year'= prices$`Principali dati`)%>% select("Region", "Year", "Prices")

new_rows <- data.frame(
  Region = rep(unique(prices$Region), each = 1),
  Year = rep(2015, length(unique(prices$Region))),
  Prices = rep(100, length(unique(prices$Region)))
)

# Combine the new rows with the original dataframe
prices <- rbind(prices, new_rows)

```

```{r}
## Poverty
Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_ <- read_excel("Individui poveri - regione di residenza (IT1,34_727_DF_DCCV_POVERTA_10,1.0) (1).xlsx")
View(Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_)
poverty <- Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_

poverty <- poverty %>% mutate(Region=poverty$...2) %>% mutate(Poverty=poverty$...3) %>% mutate(Year=poverty$`Individui poveri - regione di residenza`)
poverty<- poverty[5:201,]
poverty<- poverty %>% select("Region", "Year", "Poverty")
```

```{r}

prices$Region <- gsub("^\\[.*?\\]\\s*", "", prices$Region)
prices$Region <- gsub("^\\s+", "", prices$Region)


df<-  left_join(prices, poverty, by=c('Region', 'Year'))
df<- na.omit(df) 
```

```{r}

df$Year<-as.numeric(df$Year)
df$Prices<- round(df$Prices,0)

df <- df %>% filter(Region!='Molise'
)


```

### Descriptive statistics

```{r, fig.width=5, fig.height=3}

df_summary <- df %>%
  group_by(Year) %>%
  summarise(mean_poverty = mean(Poverty, na.rm = TRUE))  # Use na.rm = TRUE to ignore NAs

# Plot using ggplot
ggplot(data = df_summary, aes(x = Year, y = mean_poverty)) +
  geom_point() +
  labs(x = "Year", y = "Mean Poverty", title = "Mean Poverty by Year") +
  geom_area( fill="#69b3a2", alpha=0.4) +
  geom_line(color="#69b3a2", linewidth=2) +
  geom_point(size=3, color="#69b3a2") +
  theme_minimal() +
  ggtitle("Evolution of Regional Poverty in Italy")+theme(
    plot.title = element_text(size = 8),     
    plot.subtitle = element_text(size = 7),  
    plot.caption = element_text(size = 7),
     axis.title.x = element_text(size = 6),
     axis.title.y = element_text(size=6),
    legend.text = element_text(size = 6),
        legend.title = element_text(size = 7)) 
```

### Diff in Diff

```{r, fig.width=7, fig.height=3}

df2<- df %>%  filter(Year>=2018)

results<-did_multiplegt_dyn(
    df = df2,
    outcome = "Poverty",
    group = "Region",
    time = "Year",
    treatment = "Prices",
    effects = 2,
    normalized = T, 
    graph_off = F
)
 

```

```{r}
summary(results)
```

We observe a positive and significant effect of the increase in prices on regional poverty in the period from 2018 to 2019, and negative but insignificant results for the 2019-2020 period.
