---
title: "Continuos treatment"
autor: "Bertoni, Godfrin, Lim"
date:  11 February 20125
format:
  pdf: 
    fontsize: 9pt
    mainfont: Garamond
    sansfont: Garamond
editor: visual
output: 
  html_document:
    theme: cosmo
    latex_engine: pdflatex
    huxreg_options: "tabular={l|ccc}, tablewidth=0.1\\textwidth, tablefont=\\footnotesize"
    fig_caption: true
execute:
  echo: false
  warning: false
---

## Diff in Diff

```{r}
library(haven)
library(readxl)
library(tidyverse)
library(kableExtra)
Sys.setenv(RGL_USE_NULL = TRUE)

library(wooldridge)
library(DIDmultiplegtDYN)
library(huxtable)
```

```{r}
tariffs_JDE <- read_dta("C:/Users/sarah/OneDrive/Desktop/Università/Econometria/Project/TLIndonesia2015/tariffs_JDE.dta")

panel_JDE <- read_dta("C:/Users/sarah/OneDrive/Desktop/Università/Econometria/Project/TLIndonesia2015/panel_JDE.dta")


```

### Replication study

We show the estimation of the effect of banking deregulations on loans volume (data of Favara and Imbs) to showcase the methodology when there are stayers across multiple periods.

```{r}
repo <- "chaisemartinPackages/ApplicationData/main" 
file <- "favara_imbs_did_multiplegt_dyn.dta"
url <- paste("https://raw.githubusercontent.com", repo, file, sep = "/")
favara_imbs <-  haven::read_dta(url)
```

```{r, fig.width=7, fig.height=3}

results<-did_multiplegt_dyn(
    df = favara_imbs,
    outcome = "Dl_vloans_b",
    group = "county",
    time = "year",
    treatment = "inter_bra",
    effects = 8,
    placebo = 3,
    cluster = "state_n",
    normalized = F,
    same_switchers = TRUE,
    effects_equal = TRUE
)


```

```{r}
summary(results)
```

## Indonesia dataset

```{r}
#data cleaning
PNL_TrIn <- panel_JDE %>%
  mutate(tarif_In_tr = as.numeric(tarif_inp_tri),
         year = as.numeric(year),
         distid = as.numeric(distid)) %>%
    rename(TarIn = tarif_inp_tri) %>%
  select("year", "distid", "TarIn","p0", "age1660",  'hwage_e41', 'hwage_e42', 'hwage_e43', 'hwage_e44', 'hwage', 'work_e43')%>%
  drop_na() %>%
  mutate(TarIn = round(TarIn, digits=0))

#Won't display any graph as, well, too many districts. 

ChangeTrIn <- PNL_TrIn %>%
  group_by(distid) %>%
  mutate(CPY_TrIn = case_when(
    year == 1993 ~ 0,
    year == 1996 ~ (TarIn[year == 1996] - TarIn[year == 1993]),
    year == 1999 ~ (TarIn[year == 1999] - TarIn[year == 1996]),
    year == 2002 ~ (TarIn[year == 2002] - TarIn[year == 1999]),
    TRUE ~ NA_real_)) %>%
  ungroup() %>%
  mutate(CPY_TrIn = round(CPY_TrIn, digits=1))

ChangeTrInp0_Wide <- ChangeTrIn %>%
  select(distid, year, CPY_TrIn, TarIn, p0,  'hwage_e41', 'hwage_e42', 'hwage_e43', 'hwage_e44', 'hwage', 'work_e43') %>%
  pivot_wider(
    names_from = year,
    values_from = c(CPY_TrIn, TarIn,p0),
    names_glue = "{.value}_{year}")

# Stayers ? 

ChangeTrIn_Stay <- ChangeTrIn %>% 
  mutate(Stayers = ifelse(year==1999 & CPY_TrIn==0, 1, 0))

huxreg("Stayers"=lm(data=ChangeTrIn_Stay, formula= Stayers ~ 1)) %>%  set_caption('Percentage of Stayers Indonesian Dataset')


model <-lm(data=ChangeTrIn_Stay, formula= Stayers ~ 1)
names(model$coefficients)[1] = 'Stayers'
model<- huxreg(" "=model,
                  error_format = "({std.error})",
                  error_pos = "below",
                  statistics = c(N = "nobs"),
                  note = "{stars}",
                  align = "center") %>%
  set_caption('Percentage of Stayers Indonesian Dataset')


```

```{r}
# summary statistics
sum_stats_decile <- panel_JDE %>%
  select(distid, year, p0, tarif_inp_tri, hwage_e43)

sum_stats_table_decile <- data.frame(
  Statistic = c("Mean", "SD", "Min", "Max", "N Obs"),
  sapply(sum_stats_decile, function(x) c(
    mean = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    min = min(x, na.rm = TRUE),
    max = max(x, na.rm = TRUE),
    n_obs = sum(!is.na(x))
  ))
)

colnames(sum_stats_table_decile) <- c("Statistic", "District", "Year", "Poverty Headcount", "Input Tariff", "Wage (secondary education)" )
rownames(sum_stats_table_decile) <- NULL


kable(sum_stats_table_decile, caption = "Summary Statistics of Indonesian Dataset", digits = 2)%>%
  kable_classic_2(full_width = F, html_font = "Garamound") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(0, bold = T) 
```

#### Ouput: Poverty

```{r}

df_summary <- panel_JDE %>%
  group_by(year, distid) %>%
  summarise(mean_poverty = mean(p0, na.rm = TRUE))  


# Density plot for years 1996 and 1999
ggplot(data = df_summary[df_summary$year %in% c(1996, 1999),], aes(x = mean_poverty, fill = factor(year))) +
  geom_density(alpha = 0.4) +  # Add density plot with transparency
  scale_fill_manual(values = c("1996" = "#69b3a2", "1999" = "#404080")) +  # Color for each year
  labs(x = "Mean Poverty", y = "Density", title = "Density Plot of Mean Poverty by Year") +
  theme_minimal() +
  ggtitle("Density of district Poverty in Indonesia for 1996 and 1999") +
  theme(
    plot.title = element_text(size = 10),     
    plot.subtitle = element_text(size = 9),  
    plot.caption = element_text(size = 9),
    axis.title.x = element_text(size = 8),
    axis.title.y = element_text(size = 8),
    legend.text = element_text(size = 8),
    legend.title = element_text(size = 8)
  ) +
  theme(legend.title = element_blank())  # Remove legend title if needed

```

We estimate the effect of input tariff on district level poverty for the 1996-1999 period.

```{r, fig.width=7, fig.height=3}

indonesia <-ChangeTrIn %>% filter(year==1996|year==1999|year==2002)

did_multiplegt_dyn(
    df = indonesia,
    outcome = "p0",
    group = "distid",
    time = "year",
    effects=1,
    treatment = "TarIn",
    normalized = T
)


```

```{r}
summary(did_multiplegt_dyn(
    df = indonesia,
    outcome = "p0",
    group = "distid",
    time = "year",
    treatment = "TarIn",
    normalized = TRUE,
    graph_off = T
))
```

We do not find statistical significant results.

#### Output: Wage

We estimate the effect of input tariff on district level wages for level of education. We find significant results only for wages of individuals holding secondary education.

```{r}

### WAGE SECONDARY EDUCATION ONLY SIGNIFICANT WAGE
summary(did_multiplegt_dyn(
    df = indonesia,
    outcome = "hwage_e43",
    group = "distid",
    time = "year",
    treatment = "TarIn",
    normalized = TRUE,
    graph_off = T
))
```

```{r, fig.width=7, fig.height=3}

did_multiplegt_dyn(
    df = indonesia,
    outcome = "hwage_e43",
    group = "distid",
    time = "year",
    treatment = "TarIn",
    normalized = TRUE,
    graph_off = F
)
```

#### Output: Employment

We can also estimate the effect on employment, across different education levels; we do not find significant results.

```{r, fig.width=7, fig.height=3}

did_multiplegt_dyn(
    df = indonesia,
    outcome = "work_e43",
    group = "distid",
    time = "year",
    treatment = "TarIn",
    normalized = TRUE,
    graph_off = F
)
```

## Italian dataset

### 

```{r}
##Data tidying
##Prices
Principali_dati_IT1_167_742_DF_DCSP_NIC2B2015_1_1_0_1_ <- read_excel("Principali dati (IT1,167_742_DF_DCSP_NIC2B2015_1,1.0) (1).xlsx")
prices <- Principali_dati_IT1_167_742_DF_DCSP_NIC2B2015_1_1_0_1_
prices <- prices %>% mutate(Region=prices$...3)
prices<- prices[6:174,]
prices<- prices %>% mutate ('Prices'= prices$...4)%>% mutate('Year'= prices$`Principali dati`)%>% select("Region", "Year", "Prices")

new_rows <- data.frame(
  Region = rep(unique(prices$Region), each = 1),
  Year = rep(2015, length(unique(prices$Region))),
  Prices = rep(100, length(unique(prices$Region)))
)

# Combine the new rows with the original dataframe
prices <- rbind(prices, new_rows)

```

```{r}
## Poverty
Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_ <- read_excel("Individui poveri - regione di residenza (IT1,34_727_DF_DCCV_POVERTA_10,1.0) (1).xlsx")
View(Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_)
poverty <- Individui_poveri_regione_di_residenza_IT1_34_727_DF_DCCV_POVERTA_10_1_0_1_

poverty <- poverty %>% mutate(Region=poverty$...2) %>% mutate(Poverty=poverty$...3) %>% mutate(Year=poverty$`Individui poveri - regione di residenza`)
poverty<- poverty[5:201,]
poverty<- poverty %>% select("Region", "Year", "Poverty")
```

```{r}

prices$Region <- gsub("^\\[.*?\\]\\s*", "", prices$Region)
prices$Region <- gsub("^\\s+", "", prices$Region)


df<-  left_join(prices, poverty, by=c('Region', 'Year'))
df<- na.omit(df) 
```

```{r}

df$Year<-as.numeric(df$Year)
df$Prices<- round(df$Prices,0)

df <- df %>% filter(Region!='Molise'
)


```

### Descriptive statistics

```{r, fig.width=5, fig.height=3}

df_summary <- df %>%
  group_by(Year) %>%
  summarise(mean_poverty = mean(Poverty, na.rm = TRUE))  # Use na.rm = TRUE to ignore NAs

# Plot using ggplot
ggplot(data = df_summary, aes(x = Year, y = mean_poverty)) +
  geom_point() +
  labs(x = "Year", y = "Mean Poverty", title = "Mean Poverty by Year") +
  geom_area( fill="#69b3a2", alpha=0.4) +
  geom_line(color="#69b3a2", linewidth=2) +
  geom_point(size=3, color="#69b3a2") +
  theme_minimal() +
  ggtitle("Evolution of Regional Poverty in Italy")+theme(
    plot.title = element_text(size = 8),     
    plot.subtitle = element_text(size = 7),  
    plot.caption = element_text(size = 7),
     axis.title.x = element_text(size = 6),
     axis.title.y = element_text(size=6),
    legend.text = element_text(size = 6),
        legend.title = element_text(size = 7)) 
```

### Diff in Diff

```{r, fig.width=7, fig.height=3}

df2<- df %>%  filter(Year>=2018)

results<-did_multiplegt_dyn(
    df = df2,
    outcome = "Poverty",
    group = "Region",
    time = "Year",
    treatment = "Prices",
    effects = 2,
    normalized = T,
    graph_off = F
)
 

```

```{r}
summary(results)
```

We observe a positive and significant effect of the increase in prices on regional poverty in the period from 2018 to 2019, and negative but insignificant results for the 2019-2020 period.
